Fast gravitational wave parameter estimation without compromises

### 2023-02-08 src/tex/ms.tex
new bns data

\begin{figure*}
    \includegraphics[width=0.99\textwidth]{figures/GW150914.pdf}
    \caption{
      GW150914 posterior computed by our code (grey contour) and \textsc{Bilby} (blue line).
    }
    \label{fig:GW150914}
    \script{plot_GW150914.py}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.99\textwidth]{figures/GW170817.pdf}
\caption{
    GW170817 posterior computed by our code (grey contour) and \textsc{Bilby} (blue line).
}
\label{fig:GW170817}
    \script{plot_GW170817.py}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=0.99\textwidth]{figures/GW150914.pdf}
    \caption{
      GW150914 posterior computed by our code (blue) and \textsc{Bilby} (gray).
    }
    \label{fig:GW150914}
    \script{plot_GW150914.py}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.99\textwidth]{figures/GW170817.pdf}
\caption{
    GW170817 posterior computed by our code (blue) and \textsc{Bilby} (gray).
}
\label{fig:GW170817}
    \script{plot_GW170817.py}
\end{figure*}
